Estimating Gaze Duration Error Distributions from Eye Tracking Data

### 2022-06-27 paper/paper.tex
Paper update to include initial plots

We evaluate the methodology by conducting experiments over a range of AOI positions and session
lengths. The goal of which is to understand changes in the expected error profile of 
visual attention measurement when the object position varies and under variations in the
length of time that a subject is tracked.

In both instances we use an identical validation dataset generated from a panel of 15 users
engaged in a validation task after calibration with the SeeSo eye tracking software on mobile
devices. In these experiments we have used all validation data as single source of error 
estimation, but in principle these experiments could be conducted on a per user basis.

@@

@@

Not sure yet.

>>>>

We apply the gazerr application to investigate the relationship between measured gaze duration
and expected real duration under a variety of changing scenarios. These scenarios are variations
in the underlying error indicated by the eye tracking validation file and length of the session
in which the user could be looking at the area of interest.

For the sake of our simulations we use a fixed sized simulated device with viewport pixel 
dimensions of 350 by 627. Our area of interest (AOI) is a fixed position medium rectangle ad unit (MREC)
that is located toward the top of the screen. We iterate over a range of potential mean error
values (determined to be the mean Euclidean distance between the measured fixation and actual fixation).
For each of these mean error values we generate a synthetic eye tracking validation file.

We feed each of these synthetic validation files into gazerr to calculate posterior probability
distributions over true gaze duration for the set of measured gaze durations. These posterior
distributions are converted into expected values of true gaze duration for each measured duration.
We repeat the above process for multiple session lengths to investigate the impact of increasing
session length on the expected gaze duration for a fixed set of measurements.

All source code for these experiments is available in the gazerr open source package. 
Raw data is generated by running the $RUN\_EXPERIMENTS.sh$ bash script. These results
are then analysed and used to generatedt the resulting plots with the script 
$ANALYSE\_RESULTS.sh$.

@@

The first experimental result is the expected true duration against the measured duration
for a single eye tracking application with a mean fixation error of 50 pixels. These
results are shown in Figure \ref{fig:measured_vs_expected}.

\begin{figure}[h!]
\includegraphics[scale=0.5]{../results/Measured_vs_expected.png}
\caption{Measured versus expected gaze duration. MREC in 10s Session with 50px Mean Error.}
\label{fig:measured_vs_expected}
\end{figure}

The result shown in Figure \ref{fig:measured_vs_expected} is indicative of what we see under
multiple variations of the simulation configuration. At lower meaurement values there is a 
tendency for the measurement to be an over estimation, and at higher values an under-estimation.

We next examined the way that exected error in the gaze duration estimate tracks with expected 
error in the gaze fixation points. This involved calculating the mean absolute error in gaze
duration for each of the mean fixation error validation files. We performed this calculation
using two methods. The first method, called uniform, assumes that all measured values are 
equally likely. The second method, called smoothed, assumes that low measurements are much
more likely than higher measurement, and that this drop in likelihood follows an approximately
exponential distribution.

\begin{figure}[h!]
\includegraphics[scale=0.5]{../results/Fixation_vs_duration_error.png}
\caption{Fixation error versus gaze duration error.}
\label{fig:fixation_vs_duration}
\end{figure}

As shown in Figure \ref{fig:fixation_vs_duration} we see

@@
